Response to the defense feedback

### 2021-06-08 Chapter-2/Chapter-2.tex
update
Updates from Overleaf

Both hardware~\cite{Page2005PartitionedCA,
    Wang:2007:NCD:1250662.1250723,Zhang:2015:HDL:2775054.2694372,Li:2014:SLH:2541940.2541947,
    236344, 236334} and software~\cite{shih2017t,Coppens:2009:PMT:1607723.1608124,
    brickell2006software,crane2015thwarting, 197207} side-channels mitigation techniques have
been proposed recently. Hardware countermeasures, including partitioning hardware resources~\cite{Page2005PartitionedCA}, randomizing cache
accesses~\cite{Wang:2007:NCD:1250662.1250723, 236344}, and designing new
architecture~\cite{tiwari2011crafting}, require changes to complex processors and are difficult to adopt. On the contrary, software approaches are
usually easy to implement. Coppens et
al.~\cite{Coppens:2009:PMT:1607723.1608124} uses a compiler
to eliminate key-dependent control-flow transfers. Crane et
al.~\cite{crane2015thwarting} mitigates side-channels by randomizing software.
As for crypto libraries, the basic idea is to eliminate key-dependent
control-flow transfers and data accesses. Common approaches include
bit-slicing~\cite{konighofer2008fast,rebeiro2006bitslice} and unifying
control-flows~\cite{Coppens:2009:PMT:1607723.1608124}.

@@

    %\begin{table*}
    %\centering
    \caption{Many leakage detection tools are only evaluated on cryptography libraries.  All of them can not reason about the total effect of multiple leakages.}
    \label{table:side_channel_detection_tool}
    \resizebox{1\columnwidth}{!}{%

>>>>

Both hardware~\cite{Page2005PartitionedCA,
    Wang:2007:NCD:1250662.1250723,Zhang:2015:HDL:2775054.2694372,Li:2014:SLH:2541940.2541947,
    236344, 236334} and software~\cite{shih2017t,Coppens:2009:PMT:1607723.1608124,
    brickell2006software,crane2015thwarting, 197207} side-channels mitigation techniques have
been proposed recently. Hardware countermeasures, including partitioning hardware resources~\cite{Page2005PartitionedCA}, randomizing cache
accesses~\cite{Wang:2007:NCD:1250662.1250723, 236344}, and designing new
architecture~\cite{tiwari2011crafting}, require changes to complex processors and are difficult to adopt. On the contrary, software approaches are
usually easy to implement. Coppens et
al.~\cite{Coppens:2009:PMT:1607723.1608124} use a compiler
to eliminate key-dependent control-flow transfers. Crane et
al.~\cite{crane2015thwarting} mitigate side-channels by randomizing software.
As for crypto libraries, the basic idea is to eliminate key-dependent
control-flow transfers and data accesses. Common approaches include
bit-slicing~\cite{konighofer2008fast,rebeiro2006bitslice} and unifying
control-flows~\cite{Coppens:2009:PMT:1607723.1608124}.

@@

    %\begin{table*}
    %\centering
    \caption{Many leakage detection tools are only evaluated on cryptography libraries.  All of them cannot reason about the total effect of multiple leakages.}
    \label{table:side_channel_detection_tool}
    \resizebox{1\columnwidth}{!}{%
